Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer1.tex

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Cecile Cottin-Bizonne,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. 
%Changes to the manuscript from Reviewers 1 and 2 are colored in
%\textcolor{red}{red} and \textcolor{magenta}{magenta}, respectively. 
\\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei Fu, Rolf Ryham, Bryan Quaife, and Yuan-Nan Young

@@

\section*{Response to Reviewer 1}
\noindent
\comment{The manuscript discusses the self-assembly of amphiphilic Janus
particles and their dynamics in various flow conditions. Different
morphologies are recovered for different boundary conditions which are
developed by varying the hydrophobicity on Janus particle surface.
These various boundary conditions give rise to unilamellar,
multilamellar and striated structures. Finally, these structures are
subjected to linear shear flow and Taylor-Green flow. The subject of
study is interesting to soft matter community.}

\begin{itemize}
  \item {\bf Response to Summary}: We thank the Reviewer for the
    positive assessment of our manuscript. We have addressed each of the
    reviewer's comments which are summarized below.
%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

@@

\noindent
\comment{My main criticism is the following: 1. Unilamellar,
multilamellar and striated structured are subjected to various flow
conditions, with increasing shear rate or strength of the flow (for TG
case). For all structures in both flows, the main result is that these
structures break eventually either for increased shear rate or increased
flow rate. But this is expected. What do all these results mean? I feel
that a constructive message is missing.}

\begin{itemize}
  \item {\bf Response:}
  Reviewer 1 pointed out that most of the simulation runs
  corresponded to breakage in JP phases. The new Figure 3
  now includes simulation runs for shear rates ranging
  from $0$ ns$^{-1}$ to $0.1$ ns$^{-1}$ in shear flow
  and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$ in TG flow.
  These additional data allowed us to plot pre-rupture
  shear stress against shear rate in the new Figure 5
  revealing the rheological properties of the distinct
  JP phases.    
\end{itemize}

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer2.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent Dear Prof. Cecile Cottin-Bizonne,\\

\noindent Thank you for handling the manuscript.
We thank the Reviewer for their constructive feedback.
A point-by-point list of changes to the manuscript 
addressing the Reviewer's comments appears below.\\

\noindent As a summary, we have undertaken a major revision of the manuscript
that includes further detailed simulation data and analyses,
reorganized figures, and a new ``Results and Discussion'' section
written from scratch.  These changes address all the reviewers'
comments and we believe the result is a stronger manuscript.\\

\noindent
Sincerely,
\\
\noindent
Szu-Pei Fu, Rolf Ryham, Bryan Quaife, and Yuan-Nan Young

\section*{Response to Reviewer 2}

\noindent Changes appear in \textcolor{magenta}{magenta}.
(Other changes specific to Reviewers 1 appear in \textcolor{red}{red}.)\\ \\

\comment{
\noindent
I report here on the manuscript "Effects of tunable hydrophobicity on the
collective hydrodynamics of Janus particles under flows" by Szu-Pei Fu et al.
submitted for publication to Physical Review Fluids. The authors have conducted
numerical hydrodynamic simulations in 2D on the self-assembly and dynamics of
nanoscale Janus particles under simple shear flow and Taylor-Green flow using
the method of discretized boundary integrals to describe the motion of the
particles immersed in 2D Stokes flow. The Janus character of the individual
particles is realized by tuning the local hydrophobicity/hydrophilicity. The
authors have previously shown that this system forms vesicle-like structures and
investigated such structures in simple shear flow (reference [18] in the paper).
The authors now continue this work by studying different model systems by tuning
the local hydrophobicity to model (i) bilayer-forming amphiphilic particles,
(ii) formation of multilamella structures, and (iii) formation of block-chain
structures, all pre-assembled under quiescent flow conditions. These equilibrium
structures are then studied under flow of varying shear rate. The different
structures are characterized by (i) a deformation order parameter, (ii) an
orientation order parameter, and (iii) the free energy. The authors study the
dynamics of the structures under flow, when mapping to physical scales, on the
order of micro-seconds, for nanometer-sized particles and shear rates on the
order of smaller than nanoseconds$^{-1}$. The effect of shear on the conformations
is analyzed in detail, and the results are discussed with respect to related
previous literature.\\ \\
In principle I think the paper meets the criteria to be considered as an article
for Physical Review Fluids in terms of originality, quality, and presentation.
However, I am not yet convinced about the potential applicability to real
systems, as raised below:}

\begin{itemize}
  \item {\bf Response}: We thank the Reviewer for this positive appraisal of 
our manuscript. 
\end{itemize}

@@

%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}

\noindent
\comment{1) The authors study the nano-hydrodynamics around the JPs very carefully by
modeling the flow as a continuous 2D Stokes flow. While I understand that
modeling the dynamics in 2D instead of 3D is fair, i.e. their results should in
principle be extensible to 3D, my major concern is the absence of thermal
fluctuations. They are expected to be very relevant on the nanometer scale,
regarding self-assembly, dynamics and stability of the JP structures.
}

\begin{itemize}
\item {\bf Response:}
  To motivate excluding thermal fluctuations in our system,
  the new Section V.D. 
  analyzes that fluctuation Fourier spectrum 
  of a planar membrane corresponding to the Type I JP bilayer phase
  (starting on page 18).
  As the Reviewer points out, our 2D system applies
  to a transversely invariant phase with depth denoted by $L_y$.
  Equation (29) shows that the expected fluctutation is small
  relative to particle size, meaning that thermal fluctuations can
  be safely ignored when 2D system corresponds to a material that 
  is more than a few particles deep.  The elastic modulus $\kappa$ for
  Type II and Type III phases is still greater than for Type I.

  We point out though, that because the wave vector $\mathbf{k}$ is inversely
  proportional to the characteristic phase-sample size,
  fluctuation will be large provided the $L_x$ or $L_y$ is sufficiently large,
  as in the case of micron-sized vesicles.
\end{itemize}

\noindent
\comment{2) The shear rates studied are below nanoseconds$^{-1}$. What is the relevance of
such small shear rates in real (biological) systems? Furthermore, in presence of
noise, I would expect that the JP diffusive timescale is much smaller then the
shear flow time scale, and hence effectively the associated Peclet number, i.e.
importance of flow compared to noise, is negligible in this system?

Before I can recommend publication, the authors should clarify these points, in
particular justify why noise can be neglected, and why such small shear rates
are relevant.}

\begin{itemize}
\item {\bf Response:}
  In the beginning  of the new ``Results and Discussion'' Section V. (page 12),
  we now derive the range of shear rates 
  based on the capillary number $C_a$.  The derivation shows that shear forces dominate
  interfacial forces when $\dot \gamma$ exceeds
  10$^{-2}$ ns $^{-1} = 10^6$ s$^{-1}$.  Following the derivation,
  we include references to molecular dynamics simulations that also
  consider nm system sizes like ours, along with references to
  larger experimental systems were shear rates are more moderate,
  on the order of $10^3$ s$^{-1}$.  We end by calculating the
  P\'eclet number $\mathrm{Pe} = 60$, showing that
  noise is negligible compared to advection in our system.

  Although the range of simulation shear rates is unchanged in our
  revision, we thank the Reviewer as their comment has clarified
  two important points: why we chose the range of shear
  rates that we did and how neglecting noise and
  thermal fluctuation can be justified in our system.

  Reviewer 1 pointed out that most of the simulation runs
  corresponded to breakage in JP phases. The new Figure 3
  now includes simulation runs for shear rates ranging
  from $0$ ns$^{-1}$ to $0.1$ ns$^{-1}$ in shear flow
  and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$ in TG flow.
  These additional data allowed us to plot pre-rupture
  shear stress against shear rate in the new Figure 5
  revealing the rheological properties of the distinct
  JP phases. 
\end{itemize}

### 2023-04-01 doc/PRF2022/PRF_main.tex
Review2

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $2\pi \lambda \times 2\pi
\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

@@

To obtain a range for $\dot \gamma$, consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$~nm and $\kappa = 20\;\kbt$ are the characteristic phase
sample radius and bending rigidity, respectively. That is, $\kappa$
gives the elastic stress for restoring the phase-sample shape. Shear
stress overcomes elastic stress when $C_a > 1$ and this yields $\dot
\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s. Thus our values
for $\dot \gamma$ range between $0$ ns$^{-1}$ corresponding to quiescent
flow up to $0.2$~ns$^{-1}$ capable of rupturing the sample. Such shear
rates are compatible with molecular dynamics simulation
\cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA}, and shearing in blood capillary
vessels \cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.

@@

We have excluded thermal fluctuations because they are unresolved in the
JP phases we consider. For a tensionless, planar membrane, the Fourier
coefficients for the profile height $h(\xx) = \sum_{\kk} h(\kk)e^{i \kk
\cdot \xx}$ satisfy~\cite{Merath2006FluctuationSO}
\begin{equation}
\label{eq:fourier_spectrum}
\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4},
\end{equation}
where $\xx$ is a point in an $L_x \times L_y$ rectangular membrane
patch, $\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with $m,n \in
\mathbb{Z}$, not both zero, and $\kappa$ is the membrane bending
modulus.

@@

The fact that the fluctuation amplitudes are small is not a consequence
of stiffness. Quite the opposite, the value $\kappa = 20$~$\kbt$ agrees
with the experimental literature where micron sized vesicles observably
fluctuate. Rather, larger energies are required to fluctuate membranes
over smaller wavelengths and these energies exceed available thermal
energy when the wavelengths approach tens of nanometers as demonstrated
above.

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
We thank useful conversations with E.~Corona, M.~Rachh, S.~Jiang, and
  T.~Beck. B.Q.~acknowledges support from the Simons Foundation,
  Mathematics and Physical Sciences-Collaboration Grants for
  Mathematicians, Award No.~527139. Y.-N.Y.~acknowledges support from
  NSF (Grants No.~DMS 1614863 and No.~DMS 195160) and Flatiron
  Institute, part of Simons Foundation.

>>>>

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)--(b) show the average strain increase for bilayer, vesicle
  BL, multilamellar, and striated JP structures under a shear flow and a
  TG flow, respectively. Panel (c)--(d) show the average alignment of
  four JP structures under a shear flow and a TG flow, respectively.
  Each snapshot of panels (e)--(l) contains the configurations of the JP
  structure without ruptures using a specific type of boundary condition
  and the background curves indicate the velocity streamlines.}
\end{figure}
%
We subject the Type I, II, and III JP phases to background flows and
measure their material response. The background flows are a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
vertical directions, respectively. The shear flow replicates the motion
of a fluid between two parallel, moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the $\pi \lambda \times \pi
\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
phases occupy about nine cells.

@@

{\color{magenta}
To obtain a range for $\dot \gamma$, consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$~nm and $\kappa = 20\;\kbt$ are the characteristic phase
sample radius and bending rigidity, respectively. That is, $\kappa$
gives the elastic stress for restoring the phase-sample shape. Shear
stress overcomes elastic stress when $C_a > 1$ and this yields $\dot
\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s$^{-1}$. Thus our values
for $\dot \gamma$ range between $0$ ns$^{-1}$ corresponding to quiescent
flow up to $0.2$~ns$^{-1}$ capable of rupturing the sample. Such shear
rates are compatible with molecular dynamics simulation
\cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA}, and shearing in blood capillary
vessels \cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.
From the particle diffusion time $D/L^2$  
and advection time $L/u = (\dot\gamma)^{-1}$,
$D = 0.17\cdot 10^{-9}$~m$^2$~s$^{-1}$ and $L \sim 10$~nm, we 
obtain a P\'eclet number $\mathrm{Pe} = (D/L^2)/(L/u) \sim 60$,
suggesting that advection dominates the particle transport.
% L u = L^2 gammadot = 10 nm^2/ns 
% D = kBT/(6 pi mu c) = kBT/(6 pi mPa s c) 
%   = kBT/(6 pi 1e-3 N/m^2 1.25 nm) 
%   = 4 1e-12 N nm/(6 pi 1.25e-3 m^{-2} s N nm) 
%   = 0.17e-9 m^2/s
%  
% Pe = L u/D = 10 nm^2/ns/(0.17e-9 m^2/s)
%    = 59e9 1e-18 1e9 = 59
}

@@

{\color{magenta}
  We have excluded thermal fluctuations because they are unresolved in the
JP phases we consider. For a tensionless, planar membrane, the Fourier
coefficients for the profile height $h(\xx) = \sum_{\kk} h(\kk)e^{i \kk
\cdot \xx}$ satisfy~\cite{Merath2006FluctuationSO}
\begin{equation}
\label{eq:fourier_spectrum}
\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa |\kk|^4},
\end{equation}
where $\xx$ is a point in an $L_x \times L_y$ rectangular membrane
patch, $\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with $m,n \in
\mathbb{Z}$, not both zero, and $\kappa$ is the membrane bending
modulus.

@@

The fact that the fluctuation amplitudes are small is not a consequence
of stiffness. Quite the opposite, the value $\kappa = 20$~$\kbt$ agrees
with the experimental literature where micron sized vesicles observably
fluctuate \cite{D0SM00943A}.
Rather, because the wave vector $\mathbf{k}$ is inversely proportional
to the characteristic
size of $L_x$ and $L_y$, larger energies are required to fluctuate membranes
over smaller wavelengths and these energies exceed available thermal
energy when the wavelengths approach tens of nanometers as demonstrated
above.
}

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
  We thank the anonymous referees for pointing out
  the P\'eclet number, capillary number, and fluctuation analysis.
  E.~Corona, M.~Rachh, S.~Jiang, and T.~Beck
  provided useful insights.
  B.Q.~acknowledges support from the Simons Foundation,
  Mathematics and Physical Sciences-Collaboration Grants for
  Mathematicians, Award No.~527139. Y.-N.Y.~acknowledges support from
  NSF (Grants No.~DMS 1614863 and No.~DMS 195160) and Flatiron
  Institute, part of Simons Foundation.
